Formal Modelling of a Microcontroller Instruction Set in B

### 2009-06-29 trunk/papers/SBMF2009/source/paper.tex
Versão re-re-visada.

% [Conclusao] This project has many proof obligations and
The construction of then model was a difficult task, as several
iterations were needed to provide the good library definitions 
as well as to optimize the definition of the functionality of
the microprocessor instructions by grouping common data
manipulation into auxiliary functions.

However, few proof commands\footnote{The proof commands are steps that direct the
prover to find the proof, and cannot introduce false hypothesis.} need to be used
to prove most proof obligations. As there are many similar assembly instructions,
some human-directed proofs, when replayed, could discharge other proof
obligations. A good example is a set of 17 proof commands that quickly aided the
verification of 99\% (2295) of proofs WD. A new feature of B environment also
was used, the parallelization. This used four computers each one with two cores and
it increased many times the capacity of data processing. Finally, all of the
2926 proof obligations were proved using the tool support of the development
environment.

>>>>

% [Conclusao] This project has many proof obligations and
% The construction of then model was a difficult task, as several
% iterations were needed to provide the good library definitions 
% as well as to optimize the definition of the functionality of
% the microprocessor instructions by grouping common data
% manipulation into auxiliary functions.

Several iterations were needed to provide the good library definitions as well as
to fine-tune the model of the microprocessor instructions by factoring common
functionalities into auxiliary definitions.

However, few proof commands\footnote{The proof commands are steps that direct the
prover to find the proof, and cannot introduce false hypothesis.} need to be used
to prove most proof obligations. As there are many similar assembly instructions,
some human-directed proofs, when replayed, could discharge other proof
obligations. A good example is a set of 17 proof commands that quickly aided the
verification of 99\% (2295) of proofs WD. We also set up a proving environment
consisting of networked computers to take advantage of the distribution
facilities now provided in the B development environment. Finally, all of the
2926 proof obligations were proved using the tool support of the development
environment.
